The analogue method for precipitation prediction: finding better analogue situations at a sub-daily time step

### 2017-03-24 Moving temporal window - HESS/template.tex
Replacing the table for the number of analogues by a figure.

	After recalibrating, changes in the AM parameters could be observed for both the 2Z and 2Z-2MI methods. Among these, the zonal extent of the spatial windows of the circulation analogy decreased slightly (not shown). More significantly, the optimal number of analogues $N_{1}$ and $N_{2}$ increased after introducing the MTW by a considerable magnitude (Table \ref{table:analog_nb}): 25~\% to 83~\% for the 2Z method and 20~\% to 67~\% for the final selection of the 2Z-2MI method. The number of analogues $N_{1}$ of the first analogy level of the 2Z-2MI method reached three times its previous value for the Visp station ($N_{1}$~=~135 instead of 45; Table \ref{table:analog_nb}).

@@

	The performance loss resulting from the reduction of a 47~year archive (1961\textendash 2008, corresponding to the daily time series) to 25~years (1982\textendash 2007, corresponding to the hourly time series in Sect. \ref{sec:mtw}) was assessed with the original method without MTW. Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered. The AM parameters were calibrated on the original archive (see resulting analogue numbers in Table \ref{table:analog_nb}) and were used thereafter.

@@

	After the recalibration of the AMs with the MTW, the optimal analogue numbers were significantly higher than in the original methods (see Sect. \ref{sec:recalibration} and Table \ref{table:analog_nb}). As shown in Fig. \ref{fig:changes_S1}, the improvement of the S1 criterion grew along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions. It seems profitable to widen the selection of analogues in order to also keep some whose rank has increased, as they appear to be relevant to the prediction of the precipitation values. The number of good analogues was globally increased.

@@

@@

	\begin{table}[htb]
		\caption{Optimal number of analogues (of the first and second level of analogy, respectively, $N_{1}$ and $N_{2}$) of the method based on the atmospheric circulation only (method 2Z) and the method with a second level of analogy with moisture variables (2Z-2MI) on the full archive (Standard), and after recalibration using the MTW (MTW-r).}
		\begin{center}
			\begin{tabular}{l c c c c c c }
				\hline
				\multirow{3}{*}{Station} & \multicolumn{3}{c}{Standard} & \multicolumn{3}{c}{MTW-r} \\
				& 2Z & \multicolumn{2}{c}{2Z-2MI} & 2Z & \multicolumn{2}{c}{2Z-2MI}\\
				& $N_{1}$ & $N_{1}$ & $N_{2}$ & $N_{1}$ & $N_{1}$ & $N_{2}$\\ 
				\hline
				Ulrichen & 40 & 60 & 25 & 50 & 110 & 35\\
				Zermatt & 35 & 55 & 25 & 55 & 80 & 30\\
				Visp & 30 & 45 & 25 & 55 & 135 & 35\\
				Montana & 40 & 55 & 30 & 55 & 110 & 40\\
				Sion & 40 & 90 & 30 & 55 & 140 & 50\\
				Aigle & 50 & 100 & 35 & 75 & 135 & 45\\ 
				\hline
			\end{tabular}
		\end{center}	
		\label{table:analog_nb}
	\end{table}

>>>>

	After recalibrating, changes in the AM parameters could be observed for both the 2Z and 2Z-2MI methods. Among these, the zonal extent of the spatial windows of the circulation analogy decreased slightly (not shown). More significantly, the optimal number of analogues $N_{1}$ and $N_{2}$ increased after introducing the MTW by a considerable magnitude (Fig. \ref{fig:analog_nb}): 25~\% to 83~\% for the 2Z method and 20~\% to 67~\% for the final selection of the 2Z-2MI method. The number of analogues $N_{1}$ of the first analogy level of the 2Z-2MI method reached three times its previous value for the Visp station ($N_{1}$~=~135 instead of 45; Fig. \ref{fig:analog_nb}).

@@

	The performance loss resulting from the reduction of a 47~year archive (1961\textendash 2008, corresponding to the daily time series) to 25~years (1982\textendash 2007, corresponding to the hourly time series in Sect. \ref{sec:mtw}) was assessed with the original method without MTW. Both 2Z (Table \ref{table:method_2Z}) and 2Z-2MI (Table \ref{table:method_2Z-2MI}) methods were considered. The AM parameters were calibrated on the original archive (see resulting analogue numbers in Fig. \ref{fig:analog_nb}) and were used thereafter.

@@

	After the recalibration of the AMs with the MTW, the optimal analogue numbers were significantly higher than in the original methods (see Sect. \ref{sec:recalibration} and Fig. \ref{fig:analog_nb}). As shown in Fig. \ref{fig:changes_S1}, the improvement of the S1 criterion grew along with the rank of the analogue, which shows an accumulation of better analogue situations in the distributions. It seems profitable to widen the selection of analogues in order to also keep some whose rank has increased, as they appear to be relevant to the prediction of the precipitation values. The number of good analogues was globally increased.

@@

	\begin{figure}[htb]
	\includegraphics[width=7.5cm]{fig12.pdf}
	\caption{Optimal number of analogues (of the first and second level of analogy, respectively, $N_{1}$ and $N_{2}$) of the method based on the atmospheric circulation only (method 2Z) and the method with a second level of analogy with moisture variables (2Z-2MI) on the full archive (Standard), and after recalibration using the MTW (MTW-r).}
	\label{fig:analog_nb}
	\end{figure}

@@
